---
title: "P8105 HW1"
output: github_document
---
## Question 1

Load in the "moderndive" and tidyverse package.

```{r}
library(moderndive)
library(tidyverse)
```

Load in the "early_january_weather" dataset.

```{r}
data("early_january_weather")
```

### Description of dataset.

```{r}
summary(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
```

There are 358 rows and 15 columns in this dataset. 
Variables included in this dataset are year, month, day, hour, temp, dewp, humid, wind_dr, wind_speed, wind_gust, precip, pressure, visib, and time_hour.
The data was collected in 2013 during the first 15 days of January, throughout the entire 24 hours for each day.
The mean temperature is 39.58 degrees. 

### Make scatterplot

```{r}
jan_scatterplot = 
  ggplot(early_january_weather, aes(x=time_hour,y=temp,color=humid)) + geom_point()

ggsave("jan_scatterplot.pdf",jan_scatterplot,pdf)
```

The scatterplot appears to have a cyclical pattern with humidity increasing towards the right side of the graph. It appears that for each day in January, the temperature peaks at the start of the day during data collection and slowly decreases as the day progresses. The highest temperature occurs around Jan 14 while the lowest temperature occurs around the beginning of the month.

## Question 2

### Create dataframe

```{r}
df = 
  tibble(
    w = rnorm(10, sd=2),
    x = w > 0,
    y = c('a','b','c','d','e','f','g','h','i','j'),
    z = factor(c('4','3','1','16','24','18','5','9','8','2'),
              levels = c("Prime","Composite","Neither"))
  )

w = pull(df,w)
x = pull(df,x)
y = pull(df,y)
z = pull(df,z)

mean(w)
mean(x)
mean(y)
mean(z)
```

The vectors W and X returned a value when the mean() function was ran. W is a numeric variable so each element can be summed together and then divided by the total number of elements (10). X is a logical vector so when the mean() function is run, R outputs the proportion of "True" elements in the entire vector. Y and Z are not numeric or logical so the mean() function can not be applied to them. 

```{r, eval=FALSE}
as.numeric(x)
as.numeric(y)
as.numeric(z)
```

When X is converted to numeric, the "True" elements are converted to 1 and the "False" elements are converted to 0. This explains why the mean() function can work on a logical vector since R converts the elements into numeric when calculating the mean and returns the proportion of "True" in the vector. Y and Z could not be converted into numeric vectors, R only returned NA as the output which is why the mean() function did not work for these two vectors. 
