---
title: "P8105 HW1"
output: github_document
---

```{r}
library(tidyverse)
```

Let's import the 'FAS_litters.csv' csv using a relative path.

```{r}
litters_df = 
  read_csv("data/Fas_litters.csv")

litters_df = 
  janitor::clean_names(litters_df)

litters_df

```

Janitor cleans up column names by making lower case and converting to snake case

Let's import the 'FAS_litters.csv' csv using an absolute path.

```{r}
#litters_df = 
  #read_csv("~/Documents/R/Data Science/data_wrangling_1/data/FAS_litters.csv")
```
This line isn't working, come back to it later.

Let's import the 'FAS_pups.csv' csv using a relative path.

```{r}
pups_df = 
  read_csv("data/Fas_pups.csv")

pups_df = 
  janitor::clean_names(pups_df)
```

## Look at data

```{r}
litters_df # prints first 10 rows of data

head(litters_df) # prints first 6 rows of data

tail(litters_df) # prints end of the dataset
```

View the entire dataset

```{r, eval = FALSE}
view(litters_df)
```

Look at a data summary

```{r}
str(litters_df)

skimr::skim(litters_df)
```

## Options in 'read_*'

```{r}
litters_df = 
  read_csv("data/FAS_litters.csv")
#automatically assumes first row is column names and reads in data accordingly

litters_df = 
  read_csv("data/FAS_litters.csv",
           skip = 10, col_names = FALSE)
#skips first 10 rows, and does not assume first row is column names, R will assign its own names to columns

```

look at NA values

```{r}
litters_df = 
  read_csv("data/FAS_litters.csv",
           na = c("NA",19))
#assigns values as NA and re-codes the  - anywhere that has "NA" or 19 is treated as missing variable
```

Column types

```{r}
litters_df = 
  read_csv("data/FAS_litters.csv",
           col_types = 
             cols(
               Group = col_factor(),
             ))
```

